Analysis of cloud enhancement events in a 30-year record of global solar irradiance at Thessaloniki, Greece

### 2024-09-08 article/article.Rmd
Commit 2024-09-08 11:09

In this study, we investigate the characteristics of global horizontal irradiance
enhancement events induced by clouds over Thessaloniki for the period 1994 -- 2023
using data recorded every one minute.  We identified the cloud enhancement (CE)
events by creating an appropriate cloud-free irradiance reference using a radiative
transfer model and aerosol optical depth data from a collocated Cimel sun photometer
and a Brewer spectrophotometer. We found a trend in CE events of
$`r plus_sign(round(yearlyCE[var=="GLB_diff.N",slope],0))`\pm
`r round(2*yearlyCE[var=="GLB_diff.N",slope.sd],0)`\,\text{cases}/\text{year}$,
and a trend in the corresponding irradiation of
$`r plus_sign(round(yearlyCE[var=="GLB_diff.sum",slope],1))`\pm
`r round(2*yearlyCE[var=="GLB_diff.sum",slope.sd],1)`\,\text{kJ}/\text{year}$.
The peak of the CE events was observed during May and June. CE events with duration
longer than 5\nobreakspace{}min are very rare, with exceptions lasting over an hour and up to
140 minutes.  Finally, we have detected enhancements above the total solar irradiance
at the top of the atmosphere for the same solar zenith angle of up to
$400\,\text{W}/\text{m}^{2}$, with the $75\,\%$ of the cases below
$200\,\text{W}/\text{m}^{2}$. Most of these  extreme events occur in spring -- early
summer, with a secondary peak in autumn.

>>>>

In this study, we investigate the characteristics of global horizontal irradiance
enhancement events induced by clouds over Thessaloniki for the period 1994 -- 2023
using data recorded every one minute.  We identified the cloud enhancement (CE)
events by creating an appropriate cloud-free irradiance reference using a radiative
transfer model and aerosol optical depth data from a collocated Cimel sun photometer
and a Brewer spectrophotometer. We found a trend in CE events of
$`r plus_sign(round(yearlyCE[var=="GLB_diff.N",slope],0))`\pm
`r round(2*yearlyCE[var=="GLB_diff.N",slope.sd],0)`\,\text{cases}/\text{year}$,
and a trend in the corresponding irradiation of
$`r plus_sign(round(yearlyCE[var=="GLB_diff.sum",slope],1))`\pm
`r round(2*yearlyCE[var=="GLB_diff.sum",slope.sd],1)`\,\text{kJ}/\text{year}$.
The peak of the CE events was observed during May and June. CE events with duration
longer than 10\nobreakspace{}min are very rare
($<`r ceiling(100*ST_G0[,sum(GLB_ench.N>10)/.N])`\,\%$), with exceptions lasting
over an hour and up to 140 minutes.  Finally, we have detected enhancements above the
total solar irradiance at the top of the atmosphere for the same solar zenith angle
of up to
$400\,\text{W}/\text{m}^{2}$, with the $75\,\%$ of the cases below
$200\,\text{W}/\text{m}^{2}$. Most of these  extreme events occur in spring -- early
summer, with a secondary peak in autumn.

### 2024-09-08 article/article.tex
Commit 2024-09-08 10:14
Commit 2024-09-08 11:09

In this study, we investigate the characteristics of global horizontal
irradiance enhancement events induced by clouds over Thessaloniki for
the period 1994 -- 2023 using data recorded every one minute. We
identified the cloud enhancement (CE) events by creating an appropriate
cloud-free irradiance reference using a radiative transfer model and
aerosol optical depth data from a collocated Cimel sun photometer and a
Brewer spectrophotometer. We found a trend in CE events of
\(+111\pm 27\,\text{cases}/\text{year}\), and a trend in the
corresponding irradiation of \(+325.2\pm 88\,\text{kJ}/\text{year}\).
The peak of the CE events was observed during May and June. CE events
with duration longer than 5\nobreakspace{}min are very rare, with
exceptions lasting over an hour and up to 140 minutes. Finally, we have
detected enhancements above the total solar irradiance at the top of the
atmosphere for the same solar zenith angle of up to
\(400\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of the cases below
\(200\,\text{W}/\text{m}^{2}\). Most of these extreme events occur in
spring -- early summer, with a secondary peak in autumn.

@@

{\centering \includegraphics[width=1\linewidth]{../images/P-example-day-2}

>>>>

In this study, we investigate the characteristics of global horizontal
irradiance enhancement events induced by clouds over Thessaloniki for
the period 1994 -- 2023 using data recorded every one minute. We
identified the cloud enhancement (CE) events by creating an appropriate
cloud-free irradiance reference using a radiative transfer model and
aerosol optical depth data from a collocated Cimel sun photometer and a
Brewer spectrophotometer. We found a trend in CE events of
\(+111\pm 27\,\text{cases}/\text{year}\), and a trend in the
corresponding irradiation of \(+325.2\pm 88\,\text{kJ}/\text{year}\).
The peak of the CE events was observed during May and June. CE events
with duration longer than 10\nobreakspace{}min are very rare
(\(<8\,\%\)), with exceptions lasting over an hour and up to 140
minutes. Finally, we have detected enhancements above the total solar
irradiance at the top of the atmosphere for the same solar zenith angle
of up to \(400\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of the
cases below \(200\,\text{W}/\text{m}^{2}\). Most of these extreme events
occur in spring -- early summer, with a secondary peak in autumn.

@@

{\centering \includegraphics[width=1\linewidth]{../images/P-example-day-5}
